When are Fuzzy Extractors Possible?

### 2014-10-03 trunk/info-bounds/FuzzyExtPossibility.tex
change of notation, removing old intros

\section{Introduction}
Sources of reproducible secret random bits are necessary for many cryptographic applications.  In many situations, these bits are not explicitly stored for future use, but are obtained by repeating the same process  (such as reading a biometric or a physically unclonable function) that generated them the first time.
However, bits obtained this way present a problem: noise \cite{daugman2004,zviran1993comparison,brostoff2000passfaces,ellison2000protecting,mayrhofer2009shake,monrose2002password,pappu2002physical,tuyls2006puf,gassend2002silicon,suh2007physical,bennett1988privacy}.  That is, when a secret is read multiple times, readings are close~(according to some metric) but not identical.  To utilize such sources it is often necessary to remove noise, in order to derive the same value in subsequent readings.

The same problem occurs in the interactive setting, in which the secret channel used for transmitting the bits between two users is noisy and/or leaky~\cite{wyner1975wire}. Bennet, Brassard, and Robert~\cite{bennett1988privacy} identify two fundamental tasks.  The first, called information-reconciliation, removes the noise without leaking significant information. The second, known as privacy amplification, converts the high entropy secret to a uniform random value.  In this work, we consider the non-interactive version of these problems, in which these tasks are performed with a single message.

The non interactive setting is modeled by a primitive called a fuzzy extractor~\cite{DBLP:journals/siamcomp/DodisORS08}.  %Consider some distribution $W$.%The goal of a fuzzy extractor is to derive stable keys from a distribution $W$ whenever the two readings~(denoted $w$ and $w'$ respectively) are within distance $t$.  
A fuzzy extractor consists of two algorithms. The  generate algorithm ($\gen$)  takes an initial reading $w$ and produces $\key$ along with a nonsecret helper value $p$.  The reproduce~($\rep$) algorithm takes the subsequent reading $w'$ along with the helper value $p$ to reproduce $\key$.   The correctness guarantee is that the key is reproduced if the distance between $w$ and $w'$ is at most $t$.

The security requirement for fuzzy extractors that is $\key$ uniform even to an adversary who has observed $p$.   This requirement is  harder to satisfy as the allowed error tolerance $t$ increases, because it becomes easier for the adversary to guess $\key$ by guessing a $w'$ within distance $t$ of $w$ and running $\rep(w',p)$.

\paragraph{Fuzzy Min-entropy}
We introduce a new entropy notion that precisely measures how hard it is for the adversary to guess a value within distance $t$ of the original reading $w$, thus subverting security of $\key$ by running $\rep$. Suppose $w$ is sampled from a distribution $W$.   To have the maximum chance that $w'$ is within distance $t$ of $w$, the adversary would want to maximize the total probability mass of $W$ within a ball $B_t(w')$ of radius $t$ around $w'$.
We  therefore define \emph{fuzzy min-entropy} $\Hfuzz(W) \eqdef -\log \max_{w'} \Pr[W\in B_t(w')]$.

Super-logarithmic fuzzy min-entropy  is necessary for nontrivial key extraction~(\lemref{lem:fuzz necessary}). 
Most known fuzzy extractors obtain security proportional to $\Hoo(W)-\log |B_t(\cdot)|$.  \lnote{know they don't -- that's better than they achieve, because coding is not that good} \bnote{I agree but I didn't know how to introduce this value otherwise.  Seems like we need a reason to talk about $\Hoo(W) - \log |B_t|$.}
Observe that $\Hoo(W)-\log |B_t(\cdot)| \le \Hfuzz(W) \le \Hoo(W)$.  However, the lower bound is too imprecise (sometimes even negative) for practical settings.  As an example, iris scans~\cite[Section 5]{blanton2009biometric} appear to have significant $\Hfuzz(W)$ but the value $\Hoo(W) -\log |B_t|<0$.\footnote{Iris scans appear to have $\Hfuzz$ because all iris scans for different people appear to be well-spread in the metric space~\cite{daugman2006probing} and thus $\Hfuzz(W) = \Hoo(W)$.}
We ask: \emph{is fuzzy min-entropy sufficient for fuzzy extraction?}

\paragraph{Characterization  for Distribution-aware Extractability}
We show that for every source $W$ with super-logarithmic $\Hfuzz(W)$, it is possible to construct a fuzzy extractor with a super-logarithmic length $\key$ (\corref{cor:extension to fuzz ext}). We thus show that $\Hfuzz(W)$ is a necessary and sufficient condition for building a fuzzy extractor for a distribution $W$.  While our constructions are not polynomial-time (they are dependent on knowing the complete distribution of $W$), we discuss  how in related settings polynomial-time constructions that provide only computational (rather than information-theoretic) security are possible in \secref{sec:related settings}.

This characterization justifies $\Hfuzz$ as the right measure of the quality of a noisy distribution rather than relying on cruder measures such as $\Hoo(W)-\log |B_t(\cdot)|$.
It is important to note that this characterization requires the fuzzy extractor to be designed with $W$ in mind. We call such fuzzy extractors \emph{distribution aware}.

\anote{Suggested title: "Impossibility Results for Distribution-Oblivious Sketches and Extractors". Also, "typically fuzzy extractors cannot be tailored". Also "for a family of sources" $\to$ "to a family of sources".}

\paragraph{Impossibility of Fuzzy Extractors for Families of Distributions}
Typically, fuzzy extractor designs cannot be tailored to a particular source, rather they provide security for a family of sources (for example, all sources of min-entropy at least $k$ with at most $t$ errors). Making minimal assumptions about the distribution $W$ is desirable for two reasons: 1) for high entropy distributions, only a small part of the distribution has been observed 2) the adversary know some additional information about the distribution $W$ and thus the adversaries view of the distribution is different than that of the algorithm designer.

We show that this extra adversarial knowledge can be devastating  (\thref{thm:imposs fuzz ext}). 
Specifically, we show a family of distributions $\mathcal{W}$ such that no fuzzy extractor can be secure for most elements of $\mathcal{W}$.  We emphasize that each distribution $W\in \mathcal{W}$ has fuzzy min-entropy and all points in $W$ are distance at least $t$ apart. \lnote{can we say this a bit better and more precisely, by relating $\Hfuzz$ and $\Hoo$?}  For comparison with the previous setting we call this type of fuzzy extractor \emph{distribution-oblivious}.

\paragraph{Results on Information Reconciliation (Secure Sketches)}
Traditionally, fuzzy extractors use a secure sketch to perform information reconciliation~(mapping $w'$ back to $w$) and a randomness extractor~\cite{nisan1993randomness} to transform $w$ into a uniform key.  The security losses incurred in information-reconciliation dominate for most sources.\footnote{The task of privacy amplification is well-understand.  We have bounds on the length of a key extractible from a source with entropy and extractors that match this bound.}  A secure sketch is a pair of algorithms: $\sketch$ takes $w$ and produces a non secret value $ss$, $\rec$ takes $ss$ and a nearby value $w'$ and outputs the original reading $w$.

A secure sketch performs non-interactive information-reconciliation.  We show comparable results for secure sketches.  Secure sketches are possible if the distribution $W$ is precisely known~(\thref{cons:leveling}), and yet there is a family of distributions for which no secure sketch in possible~(\thref{thm:imposs sketch}). We build our distribution-aware fuzzy extractor by applying a randomness extractor to our distribution-aware secure sketch.  Our negative results for secure sketches have significantly better parameters than our negative result for fuzzy extractors.

\begin{table}
\begin{center}
\begin{tabular}{c  l l }
 & Distribution-Aware & Distribution-Oblivious\\
\hline
Secure Sketch & Yes~(\thref{cons:leveling}) & No~(\thref{thm:imposs sketch})\\
\hline
Fuzzy Extractor & Yes~(\corref{cor:extension to fuzz ext}) & No~(\thref{thm:imposs fuzz ext}) 
\end{tabular}
\end{center}
\caption{Is fuzzy min-entropy sufficient to extract a super-logarithmic length key?  Results are information-theoretic.}
\label{tab:main results}
\end{table}
\bnote{is this table doing anything or just getting in the way?  provides a quick glance to results}

@@

\begin{corollary}
\label{cor:imposs comp sketch}
Let $n$ be a security parameter and let $\mathcal{M} = |\mathbb{F}|^\gamma$.  There exists a family of distributions $\mathcal{V}$ over $\mathcal{M}$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and for any $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-HILL secure sketch $(\sketch, \rec)$ that is $(s_{sec}, \epsilon_{sec})$-hard and error $\delta$.  If 
\begin{itemize}
\item $s_{sec}\ge t(|\rec| + \gamma \log |\mathbb{F}|)$, 
\item $t\ge 4$,
\item and $\epsilon + t\delta < 1/16$,
\end{itemize}
 then $\tilde{m} =O(1)$.
\end{corollary}

@@

\section{Insufficiency of $\Hfuzz(W)$ for distribution-oblivious fuzzy extractors}
\label{sec:imposs fuzz ext}
In the previous section, we showed a family of distributions that does not admit a secure sketch.  We extend this result to fuzzy extractors.

\begin{theorem}
\label{thm:imposs fuzz ext}
Let $n$ be a security parameter.  There exists a family of distributions $\mathcal{V}$ over $\zo^n$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \kappa, t, \epsilon)$-fuzzy extractor with error $\delta = 0$, for $\kappa \ge 1$ such that $\epsilon \le 1/4 - \ngl(n)$ for $t = \omega(n^{1/2}\log n)$. \end{theorem}

\begin{proof}[Proof Outline]
Our counterexample uses a slightly different family of distributions $V$ than the counterexample for secure sketches.  In particular, we need to assume a larger error tolerance.  Let $\nu = \omega(\log n)$ and $\nu = o(n^{1/2}/\log n)$.  Let $t=4\nu n^{1/2}$ and note that $n/\nu >t$.  This family is closely related to the family we constructed in \thref{thm:imposs sketch}.  However, we work over the binary alphabet so the affine lines are ``squished'' to the binary realm.  For convenience we assume that $\nu\in\mathbb{Z}^+$.  We describe a single element $W\in V$. Let $x_1,..., x_\nu \in \zo^\nu$.  Let $\mathbb{F}$ denote the field of size $2^{\nu}$.  Let $a_2,..., a_{n/\nu}\in\mathbb{F}$ such that $a_i\neq 0$ and let $b_2,..., b_{n/\nu}\in\mathbb{F}$.  
Interpret $x_1,..., x_{\nu}$ as a element $x\in \mathbb{F}$ and let 
\[w =  \begin{pmatrix} \vec{1} \\a_1  \\ \vdots \\ a_{n/\nu} \end{pmatrix} x + \begin{pmatrix} 0  \\ 
b_2\\ \vdots \\ b_{n/\nu} \end{pmatrix} 
\]
Define the distribution $W$ as the uniform distribution over values of $x$ for a particular value of $a_2,..., a_{n/\nu}$, $b_2,..., b_{n/\nu}$.

We now present an outline for the remainder of the proof~(proofs in \apref{sec:fuzz ext proof}):
\begin{itemize}
\item \propref{prop:dist fuzzy ent fuzz}: for all $W\in \mathcal{V}$, $\Hfuzz(W) = \omega (\log n)$. Alternatively, $\forall z, \Hfuzz(V | Z=z) = \omega(\log n)$.
\item \propref{prop:dist uniform fuzz}: the distribution $V$ is uniform~(from the fuzzy extractor designer's point of view).  That is $V\overset{d}=U$.
\item \lemref{lem:fuzz can't get key}: for many values of $Z$, for a large fraction of keys, there are no viable $v\in\mathcal{M}$.  Specifically:
\begin{itemize}
\item Show that for half the keys have a bounded number of pre images in the metric space.  Denote this set as $R_{small}$.  The only viable pre images $v$ in this set are located distance $t$ from the boundary~(that is, $v$ is viable if all points in the metric space within distance $t$ map to the same key).  This means for every key $r\in R_{small}$ has bounded number of viable points in the metric space: $2^{n-n^{3/5}}$.
\item As before, there are many possible values for $z_1, z_2$ for the side information $Z$~(and these possible values are equally likely).  Furthermore, the distributions $V|Z=z_1 $ and $V| Z=z_1$ have disjoint support outside of $v$.
\item For most values of possible $Z$, the intersection between the viable pre images of $V|P \wedge Z$ and the viable pre images of $R_{small}$ is empty.  Thus, for most values of $Z$, any key lying in $R_{small}$ can be labeled as ``random''.
\end{itemize}
\item By \corref{cor:no fuzz for dist}, since no fuzzy extractor can support the uniform distribution over $\mathcal{V}$, there is distribution oblivious fuzzy extractor for the elements of $V$.
\end{itemize}

@@

\noindent
\textbf{Note:} As stated in \secref{sec:related settings}, using strong computational assumptions it is possible to avoid this result.  We note that the specific family $\mathcal{V}$, Canetti et al.~\cite[Construction 5.3]{canetti2014key} construct computational fuzzy extractors under weaker assumptions for this family of distributions when $\mathbb{F}$ is large enough.  (Their construction is stated with imperfect correctness but can be made perfect by using a code that corrects $t$ bidirectional errors instead of a code that corrects $t$ unidirectional errors.)

\paragraph{Comparison with \thref{thm:imposs sketch}} The parameters in this result are weaker than those in \thref{thm:imposs sketch}.  The major differences are that the result requires: 1) higher error tolerance $t= \omega(n^{1/2}\log n)$ 2) the fuzzy extractor must have perfect correctness.  Note ruling out a fuzzy extractor also rules out a secure sketch~(as a secure sketch can be transformed to a fuzzy extractor).  
\bibliographystyle{alpha}
\bibliography{crypto}

@@

\section{Old intros}

\subsection{Ben's text from Wed afternoon, incorporated into the above}

Intuitively, error-tolerance and key strength are at odds.  Fix some distribution $W$.  The adversary has access to the reproduce function and attempts to learn the key by inputting a point.  Let $x^*$ be the point input by the adversary, the adversary learns the correct key whenever $\dis(w, x^*)\le t$.  For security, this must occur with negligible probability.  That is, a negligible portion of the probability mass of $W$ may be close to any point in the metric space.  Mathematically, for all $x^*, \sum_{w\in W | \dis(w, x^*)\le t} \Pr[ W= w] \le \ngl(n)$.  We call the negative logarithm of this quantity the \emph{fuzzy min-entropy} of a distribution.  A distribution must have super-logarithmic fuzzy min-entropy for a fuzzy extractor or a secure sketch  to provide meaningful security~(\lemref{lem:fuzz necessary}).  
We ask:  \emph{is fuzzy min-entropy sufficient for key derivation from noisy sources}?

We have evidence for the sufficiency of fuzzy min-entropy. In the interactive setting, fuzzy min-entropy is sufficient for both tasks under mild computational assumptions.  In the non-interactive setting, semantically secure multi-linear maps allow for strong key derivation.  We provide evidence it is possible under strong assumptions on the knowledge of $W$.  Thus, one might hope that  information-theoretic fuzzy extraction is possible for all distributions with fuzzy min-entropy.

\paragraph{Main result}
Our main result is negative~(\thref{thm:imposs fuzz ext}) is negative: fuzzy extractors are impossible if the distribution $W$ is unknown.   Fuzzy extractors normally assume partial knowledge of a distribution $W$, assuming it comes from a family of distributions $\mathcal{W}$.  We show a family of distributions $\mathcal{W}$ such that no instantiation can be secure for all elements of $\mathcal{W}$.  Each possibility for the distribution $W$ has fuzzy min-entropy and its points are far apart~(intuitively, this should make the task easier).

\paragraph{The cost of distributional uncertainty}
Fuzzy extractors are designed with limited knowledge of the target distribution.  Traditionally, the distribution $W$ is assumed to be an arbitrary distribution with min-entropy.  Making minimal assumptions about the distribution $W$ is desirable for two reasons: 1) for high entropy distributions, only a small part of the distribution has been observed 2) the adversary may have some side information about the distribution $W$ and thus the adversaries view of the distribution is different than that of the algorithm designer.

Our negative results show that when the distribution $W$ is sufficiently unknown, fuzzy extractors are impossible.  To illustrate that distributional uncertainty is the real problem, we define a restricted form of fuzzy extractor that is allowed to know the exact distribution $W$.  We call this a \emph{distribution-aware} fuzzy extractor.  In this setting, fuzzy min-entropy is a sufficient condition for key derivation~(\corref{cor:extension to fuzz ext}).

\subsection{Old organization}

\lnote{I am thinking the sketch paragraph should go later, after necessary condition, b/c the necessary condition is for F.E.}

Traditionally, fuzzy extractors use a secure sketch to perform information reconciliation~(mapping $w'$ back to $w$) and a randomness extractor~\cite{nisan1993randomness} to transform $w$ into a uniform key.  The security losses incurred in information-reconciliation dominate for most sources.\footnote{The task of privacy amplification is well-understand.  We have bounds on the length of a key extractible from a source with entropy and extractors that match this bound.}  A secure sketch is a pair of algorithms: $\sketch$ takes $w$ and produces a non secret value $ss$, $\rec$ takes $ss$ and a nearby value $w'$ and outputs the original reading $w$.  
Known constructions of fuzzy extractors and secure sketches incur significant losses.  In particular, for most practical noisy sources, there are no known secure sketches or fuzzy extractors.  In this work, we ask whether this is inherent.  We identify a key problem: uncertainty in the distribution of $W$.

\paragraph{A Necessary Condition:}  Intuitively, error-tolerance and key strength are at odds.  Fix some distribution $W$.  The adversary has access to the reproduce function and attempts to learn the key by inputting a point.  Let $x^*$ be the point input by the adversary, the adversary learns the correct key whenever $\dis(w, x^*)\le t$.  For security, this must occur with negligible probability.  That is, a negligible portion of the probability mass of $W$ may be close to any point in the metric space.  Mathematically, for all $x^*, \sum_{w\in W | \dis(w, x^*)\le t} \Pr[ W= w] \le \ngl(n)$.  We call the negative logarithm of this quantity the \emph{fuzzy min-entropy} of a distribution.  A distribution must have super-logarithmic fuzzy min-entropy for a fuzzy extractor or a secure sketch  to provide meaningful security~(\lemref{lem:fuzz necessary}).

\lnote{The below needs a title and clearer form: ``When is the necessary condition sufficient?'' Two answers, both computational: general MPC under relatively benign assumptions but interaction or obfuscation with crazy assumptions but no interaction}

Consider a user, Alice, using a noisy secret to authenticate with a remote server, Bob.  In this setting, Alcie could initially send the value $w$ to Bob and then authenticate with subsequent value $w'$.  If the server holds $w$ and the user $w'$ the two parties can agree on a key using an interactive protocol.\footnote{It is dangerous to allow a remote server access to original reading $w$ as they can then impersonate the user.  Ideally, the server would keep a ``hashed'' value of $w$.  This is  done for noiseless secrets like passwords.}  In this world, secure two-party computation can produce a key whenever the distribution $W$ has fuzzy min-entropy.
In the one-message setting, we are far from this ideal. \lnote{Why frame it this way, effectively introducing a new scenario, when we could appeal to the first paragraphs of the intro and simply say ``consider, for a moment, removing the requirement that these tasks are performed with a single message''? Also a paper to cite: ``Secure computation w/o authentication'' by some superset of Canetti and Rabin; the reason we should cite this one rather than general MPC is that we don't want to assume authenticated channels here to start with}

\lnote{I don't think you want to talk about traditional constructions here yet. I think what you want to say, in light of the previous computational paragraph, is ``what about information-theoretic: is the necessary condition also sufficient''?}

Traditional fuzzy extractors and secure sketches operate in the worst case and incur entropy loss of the size of the ball to be error-corrected.  This loss is usually linear in the input length of the string.  While, this is optimal for the uniform distribution, it is far from optimal for distributions that arise in practice.  As an example, many examples that arise in practice there are more error patterns than starting entropy.  Traditional fuzzy extractors provide no guarantee for sources of this type.  The work of Canetti et al.~\cite{canetti2014key} constructs fuzzy  extractors for some distributions with more errors than entropy.  This leads to the following natural question: \emph{when is key derivation from noisy sources possible?}  To help answer this question, we identify a key problem: uncertainty in the distribution of $W$.

\paragraph{The price of distributional uncertainty}

\lnote{I think this should be ``Our Contributions'' and go in the following order. Our main contribution is to show that, if your FE works for a sufficiently rich class of distributions, this condition is not sufficient. On the other hand, in the extreme case of custom-building for a totally known distribution, we show (non-poly-time) construction that works. We also consider the same question for what has traditionally been the main building block of FE, ``secure sketch'' (appeal to the already-defined-above notion of information reconciliation and introduce the briefly). We show an even tighter impossibility result for FE, as well as (non-poly-time) possibility result}

The question of whether the necessary condition is also sufficient depends on the class of distributions for which your construction needs to work. First, negative result (which is most important)

Fuzzy extractors are designed with limited knowledge of the distributions that will later be used.  Traditionally, the distribution $W$ is assumed to be an arbitrary distribution with min-entropy.  Making minimal assumptions about the distribution $W$ is desirable for two reasons: 1) for high entropy distributions, only a small part of the distribution has been observed 2) the adversary may have some side information about the distribution $W$ and thus the adversaries view of the distribution is different than that of the algorithm designer.  Fuzzy extractors support a family of distributions $\mathcal{W}$ and hope that the target distribution $W\in\mathcal{W}$.

>>>>

\section{Introduction}
Sources of reproducible secret random bits are necessary for many cryptographic applications.  In many situations these bits are not explicitly stored for future use, but are obtained by repeating the same process  (such as reading a biometric or a physically unclonable function) that generated them the first time.
However, bits obtained this way present a problem: noise \cite{daugman2004,zviran1993comparison,brostoff2000passfaces,ellison2000protecting,mayrhofer2009shake,monrose2002password,pappu2002physical,tuyls2006puf,gassend2002silicon,suh2007physical,bennett1988privacy}.  That is, when a secret is read multiple times, readings are close~(according to some metric) but not identical.  To utilize such sources, it is often necessary to remove noise, in order to derive the same value in subsequent readings.

The same problem occurs in the interactive setting, in which the secret channel used for transmitting the bits between two users is noisy and/or leaky~\cite{wyner1975wire}. Bennet, Brassard, and Robert~\cite{bennett1988privacy} identify two fundamental tasks.  The first, called information reconciliation, removes the noise without leaking significant information. The second, known as privacy amplification, converts the high entropy secret to a uniform random value.  In this work, we consider the noninteractive version of these problems, in which these tasks are performed together with a single message.

The noninteractive setting is modeled by a primitive called a fuzzy extractor~\cite{DBLP:journals/siamcomp/DodisORS08}, which consists of two algorithms.  %Consider some distribution $W$.%The goal of a fuzzy extractor is to derive stable keys from a distribution $W$ whenever the two readings~(denoted $w$ and $w'$ respectively) are within distance $t$.   T
The  generate algorithm ($\gen$)  takes an initial reading $w$ and produces an output $\key$ along with a nonsecret helper value $p$.  The reproduce~($\rep$) algorithm takes the subsequent reading $w'$ along with the helper value $p$ to reproduce $\key$.   The correctness guarantee is that the key is reproduced precisely as long as the distance between $w$ and $w'$ is at most $t$.

The security requirement for fuzzy extractors that is $\key$ uniform even to a (computationally unbounded) adversary who has observed $p$.   This requirement is  harder to satisfy as the allowed error tolerance $t$ increases, because it becomes easier for the adversary to guess $\key$ by guessing a $w'$ within distance $t$ of $w$ and running $\rep(w',p)$.

\paragraph{Fuzzy Min-entropy}
We introduce a new entropy notion that precisely measures how hard it is for the adversary to guess a value within distance $t$ of the original reading $w$, thus subverting the security of $\key$ by running $\rep$. Suppose $w$ is sampled from a distribution $W$.   To have the maximum chance that $w'$ is within distance $t$ of $w$, the adversary would want to maximize the total probability mass of $W$ within the ball $B_t(w')$ of radius $t$ around $w'$.
We  therefore define \emph{fuzzy min-entropy} $\Hfuzz(W) \eqdef -\log \max_{w'} \Pr[W\in B_t(w')]$.  Observe that this quantity can be bounded in terms of min-entropy: $\Hoo(W) \le \Hfuzz(W) \le \Hoo(W)-\log |B_t(\cdot)|$ with equality when $t=0$.

Super-logarithmic fuzzy min-entropy  is \emph{necessary} for nontrivial key extraction~(we show this in  \lemref{lem:fuzz necessary}, which formalizes the above intuition). 
However, existing constructions do not measure their security in terms of fuzzy min-entropy; instead, their security is shown to be  $\Hoo(W)$ minus some loss that is at least $\log |B_t(\cdot)|$ due to error-tolerance. Since $\Hoo(W)-\log |B_t(\cdot)| \le \Hfuzz(W)$, it is natural to ask whether this loss is necessary. This question is particularly relevant when the gap between the two sides of the inequality is high.  As an example, iris scans appear to have significant $\Hfuzz(W)$ (because iris scans for different people appear to be well-spread in the metric space~\cite{daugman2006probing}) but negative $\Hoo(W) -\log |B_t|$ \cite[Section 5]{blanton2009biometric}. We therefore ask: \emph{is fuzzy min-entropy sufficient for fuzzy extraction?} There is evidence that it may be when the security requirement is computational rather than information-theoretic---see \secref{sec:related settings}.

\paragraph{Tight Characterization for the Case of a Known Distribution}
We show that for every source $W$ with super-logarithmic $\Hfuzz(W)$, it is possible to construct a fuzzy extractor with a super-logarithmic length $\key$ (\corref{cor:extension to fuzz ext}). We thus show that $\Hfuzz(W)$ is a necessary and sufficient condition for building a fuzzy extractor for a distribution $W$.  It is important to emphasize that these constructions incorporate the knowledge of the complete distribution of $W$ (and, in particular, they are not polynomial-time).

This characterization justifies $\Hfuzz$ as the right measure of the quality of a noisy distribution,  better than cruder measures such as $\Hoo(W)-\log |B_t(\cdot)|$.

\paragraph{Impossibility of Fuzzy Extractors for Families of Distributions}
Assuming full knowledge of a distribution is often unrealistic. Indeed, high-entropy distributions can never be fully observed directly and must therefore be modeled. It is imprudent to assume that the designer's model of a distribution is completely accurate---the adversary, with greater resources, would likely be able to build a better model. Therefore, fuzzy extractor designs cannot usually be tailored to one  particular source. Existing designs work for a family of sources (for example, all sources of min-entropy at least $k$ with at most $t$ errors). Thus, the design is fixed before the distribution is fully known, and the adversary may therefore know more about the distribution than the designer of the fuzzy extractor.

We show that this extra adversarial knowledge can be devastating  (\thref{thm:imposs fuzz ext}). 
Specifically, we show a family of distributions $\mathcal{W}$ such that not even a 1-bit fuzzy extractor can be secure for most distributions in  $\mathcal{W}$.  We emphasize that each distribution $W\in \mathcal{W}$ has superlogarithmic fuzzy min-entropy---in fact, $\Hfuzz(W)=\Hoo(W)$, because all points in $W$ are distance at least $t$ apart. Our proof relies on high dimensionality of $W$ and on perfect correctness of the $\rep$ procedure.

\begin{table}[h]
\begin{center}
\begin{tabular}{c  l l }
 & Known Distribution & Family of Distributions\\
\hline
Secure Sketch & Yes~(\thref{cons:leveling}) & No~(\thref{thm:imposs sketch})\\
\hline
Fuzzy Extractor & Yes~(\corref{cor:extension to fuzz ext}) & No~(\thref{thm:imposs fuzz ext}) 
\end{tabular}
\end{center}
\caption{Is fuzzy min-entropy sufficient to extract a super-logarithmic length key?  Results are information-theoretic.}
\label{tab:main results}
\end{table}

\paragraph{Stronger Results on Information Reconciliation (Secure Sketches)}
Traditionally, fuzzy extractors use a secure sketch to perform information reconciliation~(mapping $w'$ back to $w$), followed by randomness extractor~\cite{nisan1993randomness} to transform $w$ into a uniform key.  The security losses incurred in the first of these two steps dominate for typical sources and, indeed, this step is less well understood.\footnote{Randomness extractors have matching upper and lower bounds on the security loss: for every extra two bits of output key, they lose one bit of security} Formally, a secure sketch performs non-interactive information reconciliation via pair of algorithms: $\sketch$ takes $w$ and produces a nonsecret value $ss$, while $\rec$ takes a value $w'$ within distance $t$ of $w$ and uses $\sketch$ to output the original reading $w$.

We show comparable, but stronger, results for secure sketches.  Namely, we show in \thref{cons:leveling} that secure sketches are possible if the distribution $W$ is precisely known. (In fact, we obtain our fuzzy extractors for the case of a known distribution from this result by simply applying a randomness extractor.) On the other hand, there is a family of sources with superlogarithmic $\Hfuzz=\Hoo$ for which no secure sketch correcting even a few errors is possible~(\thref{thm:imposs sketch}). The impossibility result applies even when $\rec$ is allowed to be incorrect with probability up to $1/4$ (as opposed to our fuzzy extractor impossibility result).

@@

\begin{corollary}
\label{cor:imposs comp sketch}
Let $n$ be a security parameter and let $\mathcal{M} = |\mathbb{F}|^\gamma$.  There exists a family of distributions $\mathcal{W}$ over $\mathcal{M}$ such that for each element $W\in \mathcal{W}$, $\Hfuzz(W)= \omega(\log n)$ and for any $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-HILL secure sketch $(\sketch, \rec)$ that is $(s_{sec}, \epsilon_{sec})$-hard and error $\delta$.  If 
\begin{itemize}
\item $s_{sec}\ge t(|\rec| + \gamma \log |\mathbb{F}|)$, 
\item $t\ge 4$,
\item and $\epsilon + t\delta < 1/16$,
\end{itemize}
 then $\tilde{m} =O(1)$.
\end{corollary}

@@

\section{Insufficiency of $\Hfuzz(W)$ for distribution-oblivious fuzzy extractors}
\label{sec:imposs fuzz ext}
In the previous section, we showed a family of distributions that does not admit a secure sketch.  We provide a similar result for fuzzy extractors.

\begin{theorem}
\label{thm:imposs fuzz ext}
Let $n$ be a security parameter.  There exists a family of distributions $\mathcal{W}$ over $\zo^n$ such that for each element $W\in \mathcal{W}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{W}, \kappa, t, \epsilon)$-fuzzy extractor with error $\delta = 0$, for $\kappa \ge 1$ such that $\epsilon \le 1/4 - \ngl(n)$ for $t = \omega(n^{1/2}\log n)$. \end{theorem}

\begin{proof}[Proof Outline]
Our counterexample uses a slightly different family of distributions $\mathcal{W}$ than the counterexample for secure sketches.  In particular, we need to assume a larger error tolerance.  Let $\nu = \omega(\log n)$ and $\nu = o(n^{1/2}/\log n)$.  Let $t=4\nu n^{1/2}$ and note that $n/\nu >t$.  We work over the binary alphabet so we squish affine lines to the binary realm.  Let $x_1,..., x_\nu \in \zo^\nu$.  Let $\mathbb{F}$ denote the field of size $2^{\nu}$.  Let $a_2,..., a_{n/\nu}\in\mathbb{F}$ such that $a_i\neq 0$ and let $b_2,..., b_{n/\nu}\in\mathbb{F}$.  
Interpret $x_1,..., x_{\nu}$ as a element $x\in \mathbb{F}$ and let 
\[w =  \begin{pmatrix} \vec{1} \\a_2  \\ \vdots \\ a_{n/\nu} \end{pmatrix} x + \begin{pmatrix} 0  \\ 
b_2\\ \vdots \\ b_{n/\nu} \end{pmatrix} 
\]
Define the distribution $W$ as the uniform distribution over values of $x$ for a particular value of $a_2,..., a_{n/\nu}$, $b_2,..., b_{n/\nu}$.  
Let $\mathcal{W}$ be the set of all such $W$.  Let $V$ be the uniform distribution over elements $\mathcal{W}$ and $Z$ is the description of the line $Z = a_2,..., a_{n/\nu}, b_2, ..., b_{n/nu}$.
We now present of the proof~(proofs in \apref{sec:fuzz ext proof}):
\begin{itemize}
\item \propref{prop:dist fuzzy ent fuzz}: for all $W\in \mathcal{W}$, $\Hfuzz(W) = \omega (\log n)$. Alternatively, $\forall z, \Hfuzz(V | Z=z) = \omega(\log n)$.
\item \propref{prop:dist uniform fuzz}: the distribution $V$ is uniform.
\item \lemref{lem:fuzz can't get key}: for many values of $Z$ and for half the keys $r\in\zo^\kappa$, there are no viable $v\in\mathcal{M}$.  Specifically:
\begin{itemize}
\item Show that for half the keys have a bounded number of pre images in the metric space.  Denote this set as $R_{small}$.  
\item Consider some $r\in R_{small}$.  %Our goal is to show there are few values of $v \in V|Z$ that could produce this key.  
Consider the set of $V_{r} = \{w | \rep(w, p) = r\}$.  The only values of $V_r$ that could be the real value of $w$ are distance $t$ from a boundary of $V_r$~(the functionality of $\rep$ guarantees that for the true $w$ all nearby points map to the same $r$).  We show that most of $V_r$ is near a boundary.  Harper's theorem says that the boundary of a region is minimized by a ball containing the same number of points~\cite{harper1966optimal} .  Hoeffding's inequality says that most of a ball lies near its boundary~\cite{hoeffding1963probability}.  Together these two results imply that $V_r$ is small.
\item As before, there are many possible values for $z_1, z_2$ for the side information $Z$~(and these possible values are equally likely).  Furthermore, the distributions $V|Z=z_1 $ and $V| Z=z_1$ have disjoint support outside of $v$.
\item For most values of possible $Z$, the intersection between the viable pre images of $V|Z$ and $V_r$ is empty.  Thus, for most values of $Z$, any key lying in $R_{small}$ can be labeled as ``random''.
\end{itemize}
\item By \corref{cor:no fuzz for dist}, since no fuzzy extractor can support the uniform distribution over $\mathcal{W}$, there is distribution oblivious fuzzy extractor for the elements of $\mathcal{W}$.
\end{itemize}

@@

\noindent
\textbf{Note:} As stated in \secref{sec:related settings}, using strong computational assumptions it is possible to avoid this result.  We note that the specific family $\mathcal{W}$, Canetti et al.~\cite[Construction 5.3]{canetti2014key} construct computational fuzzy extractors under weaker assumptions for this family of distributions when $\mathbb{F}$ is large enough.  (Their construction is stated with imperfect correctness.  A construction with perfect correctness is obtained by using a code that corrects $t$ bidirectional errors instead of a code that corrects $t$ unidirectional errors.)

\paragraph{Comparison with \thref{thm:imposs sketch}} The parameters in this result are weaker than those in \thref{thm:imposs sketch}.  The major differences are that the result requires: 1) higher error tolerance $t= \omega(n^{1/2}\log n)$ 2) the fuzzy extractor must have perfect correctness.  Note ruling out a fuzzy extractor also rules out a secure sketch~(as a secure sketch can be transformed to a fuzzy extractor).  
\bnote{improve this}
\bibliographystyle{alpha}
\bibliography{crypto}

@@

\section{Leveraging convex combinations?}
\label{sec:convex comb}
In many situations solving a problem for min-entropy distributions can be reduced to solving the problem for flat distributions and then using the fact that any min-entropy distribution is a convex combination of flat distributions.  For example, consider the following hypothetical extension to \consref{cons:universal hash}.  Let $W$ be some distribution that is a finite convex combination of flat sources $W_1,..., W_n$ where each $\forall i, \Hoo(W_i)\ge k$.\footnote{A distribution may be an  convex combination of an infinite number of distributions.  However, the difficulty arises even when considering a finite combination so we restrict ourselves to this simpler case.}  For convenience we assume that the coefficients on all $W_i$ are the same and distributions may be repeated.
